---
title: "farsMaps: Analyse and Plot Road-Fatality Data"
author: "Russell Hyde"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview
This package contains functions and data for reading-in, summarizing and 
plotting out data from the "Fatality Analysis Reporting System" project.

To import the package run:

```{r}
# devtools::install_github("russHyde/farsMaps")
library("farsMaps")
```

# I/O Functions
To read in FARS data from a particular year (data for 2013-2015 are provided 
with the package), run the following:

```{r}
fars_data <- fars_read_years(2013:2014)
```

The imported datasets contain a MONTH and a year column.
```{r}
head(fars_data)
```

# Summary Functions
To summarise the fatalities in a given year, run the following:
```{r}
fars_summary <- fars_summarize_years(2013:2015)
```

This summarises the number of fatalities per month in each year (across all
available states).

```{r}
fars_summary
```

# Plotting Functions
To plot the locations of the fatalities in a given state for a particular
year, the user should provide an integer to indicate the required state,
and the year required. For example,

```{r}
fars_map_state(10, 2013)
```
